\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-31 paper/ms.tex
RJObject prior
wrap and log-uniform prior

@@

>>>>

In the example, the proposal for $\sigma$ is implemented by taking advantage
of the uniform prior for $\ln(\sigma)$. So $\sigma$ is transformed by
taking a logarithm, a proposal move is made (that satisfies detailed balance
with respect to a uniform distribution), and then $\sigma$ is exponentiated
again. The step for the uniform prior between -10 and +10
uses the following code:
\begin{CodeChunk}
\begin{CodeInput}
sigma += 20.0*rng.randh();
DNest4::wrap(sigma, -10.0, 10.0);
\end{CodeInput}
\end{CodeChunk}
The factor of 20 accounts for the prior width, and
the \code{wrap(double\&, double, double)} function uses the modulo operator
to construct periodic boundaries. For example, if the perturbation results
in a value of 10.2, which is outside the prior range, the value is modified to
$-9.8$.
The \code{wrap} function has no return value and works by modifying its
first argument, which is passed by reference.

@@

If $N$ is the number of components, $\boldsymbol{x}_i$ is the parameters
of the $i$th component, and $\alpha$ is the hyperparameters, the prior
can be factorised as
\begin{align}
p\left(N, \alpha, \left\{\boldsymbol{x}_i\right\}_{i=1}^N\right)
&= p(N)p(\alpha | N)p\left(\left\{\boldsymbol{x}_i\right\}_{i=1}^N | \alpha, N\right).
\end{align}
The specific assumptions of \pkg{RJObject} are
\begin{align}
p\left(N, \alpha, \left\{\boldsymbol{x}_i\right\}_{i=1}^N\right)
&= p(N)p(\alpha)p\left(\left\{\boldsymbol{x}_i\right\}_{i=1}^N | \alpha\right).
\end{align}
which is depicted in Figure~\ref{fig:rjobject_pgm}.
